---
title: "Ethics 9-3-21"
subtitle: "Moral Relativism, Isolationism, Absolutism"
author: ""
institute: Department of Philosophy 
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
---

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_mono_accent(
  base_color = "#1c5253",
  header_font_google = google_font("Josefin Sans"),
  text_font_google   = google_font("Montserrat", "300", "300i"),
  code_font_google   = google_font("Fira Mono")
)
style_duo_accent_inverse(primary_color = "#035AA6", secondary_color = "#03A696")
```
```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(dev = 'svg')
options(device = function(file, width, height) {
  svg(tempfile(), width = width, height = height)
})
library(tidyverse)
library(stevemisc)

```
```{r broadcast, echo=FALSE}
xaringanExtra::use_broadcast()
```
```{r embed-xaringan, echo=FALSE}
xaringanExtra::embed_xaringan(url = "/home/redapemusic35/1-prospecti/xaringan-example/presentations/share-again.html", ratio = "4:3")
```
```{r share-again, echo=FALSE}
xaringanExtra::use_share_again()
```

```{r, load_refs, include=FALSE, cache=FALSE}
library(RefManageR)
BibOptions(check.entries = FALSE,
           bib.style = "authoryear",
           cite.style = "alphabetic",
           style = "text",
           hyperlink = TRUE,
           dashed = FALSE)
myBib <- ReadBib("/home/redapemusic35/1-prospecti/references.bib", check = FALSE)
```
---

# Moral Relativism and Isolationism 

> We cannot critic other cultures because we will never understand them well enough to make judgments about them *and* the values of respect and tolerance forbids us to take up a critical position to any other culture.

--

1. We can understand other cultures.

--

2. Relativism is not a respectful attitude towards other cultures

--

3. Others can criticize our own culture

--

4. Moral relativism allows us to praise other cultures so why not criticize?

???

1. Because no one can respect what is unintelligible to them. To respect someone, we have to know enough about them to make a favorable judgment.
2. But we cannot know enough about Japanese Samurai culture, so we cannot extol the virtues of Japanese Samurai, unless we can.
3. Both missionaries and anthropologists are outsiders. One typically praises while the other criticizes.
4. If we cannot blame other cultures, how can we blame our own? According to the isolationist, we cannot. But this blocks social progress.

---

# Six More Problems with Ethical Relativism

--

1. No criticism or praise of other cultures

--

2. Majority Rule

--

3. Professed or Actual Morality?

--

4. What is a Majority?

--

5. How do we define a culture?

--

6. Can tolerance be a universal value?

---

class: center, middle

1. cultural relativism

--

2. ethical relativism

---

class: center, middle

> One is making an observation while the declaring a norm. "Ethical relativism is a *normative* theory that states there is no universal moral code." (123). As such, practices cannot be criticized because there is not universal standard with which to criticize them by.

```{r, echo=F, results="asis"}

Cite(myBib, "rose19")
```

---

# Absolutism

--

> The idea of something's being good, not according to some standard but just by possessing a property of goodness, does not even make much sense. If some standard were special, were the right one, then something could be good absolutely by being good relative to that standard. 


```{r, echo=F, results="asis"}
Citet(myBib, "drei06")

```

???


---

## Context, Standard and Non-Standard

--

* A good clock tells time accurately. 

--

* Astronomers? 

--

* Shepherds?

???

- tells time accurately
- a stopped clock cannot be good, doesn't tell time accurately
- relative to astronomy
- takes care of his sheep
---

class: center, middle

1. Standards come in contexts, their goodness is good relative to some function.

---

# Example of Function

> An adult shaped to the drives and standards of either of these cultures, if he were transported into our civilization, would fall into our categories of abnormality.

--

1. No societal mores can be used across the whole potential range of human behavior.

--

2. Just like language, there is innumerable phonetic possibility, articulations and the possibility of language depends on a selection and standardization of a few of these.

--

3. Similarly, organized behavior too, depends on a similar selection among possible behavior traits.



???

Not sure about the accuracy of this story. Written in 1934 by an anthropologist. Not sure if own beliefs influenced perception of the villagers.

Story of Melansian culture displaying extreme fears of poisoning by Ruth Benedict (1934) "Anthropology and the Abnormal"

Tribe looks on one another as skilled manipulators of black magic. Therefore, to protect their harvests, they guard their crop seeds. Sharing in this culture is seen as abnormal. Christian missionary was deemed insane for his generosity.

Some behaviors are selected for, others are not and not sure why.


---

class: center, middle

```{r, echo=F, eval=T}
library(DiagrammeR)
grViz(" 
  digraph {
    # Multiple level nodes
    node [shape = square, color=CornflowerBlue]
    A [label = 'A']; 
    0 [label = '0', shape = none];
    B [label = 'B'];
    1 [label = '1', shape = none];
    Reject [label = '1 - x, x', shape = none];
    N;
    Awins [shape = none, label = 'beH k, beH L'];
    Bwins [shape = none, label = '-k, 1 - k']



     # Connect nodes with edges and labels
    A -> 0 [arrowhead= none]
    A -> B
    A -> 1 [arrowhead = none]
    B -> Reject [headlabel = 'Reject', labeldistance = 5, labelangle=75] 
    B -> N [label = '       Reject']
    N -> Awins [headlabel = 'A wins (1 - p)', labeldistance=4.5 ,
        labelangle=75]
    N -> Bwins [label = 'B wins (p)']
  }

[1]: 'A' 
[2]: '0'
[3]: paste0('Model 3\\n Split 3') 
[4]: paste0('Model 6\\n Split 4') 
")

```

---

# But normality is synonymous with good

|                         | Sheena Easton Stays Home       | Sheena Easton Goes to Baby's Work |
|-------------------------|---------------------|------------------|
| **Baby Home Again**          |  -100, **100**         |  **100**, 0       |
| **Baby Stays at Work**             |   **50**, 0        |  -100, **100**        |

--

<br />

Notice we have no pure strategies, and no Nash equilibrium.

- Sheena Easton wants to proverbially "match pennies."
- Her baby has diametrically opposed preferences, fearing for his safety.

Solution: mixed strategy.

---

Here's behavioral selection chart.

```{r, echo=F, eval=T}
library(DiagrammeR)
grViz(" 
  digraph {
    # Multiple level nodes
    node [shape = square, color=CornflowerBlue]
    A [label = 'A']; 
    0 [label = '0', shape = none];
    B [label = 'B'];
    1 [label = '1', shape = none];
    Accept [label = '1 - x, x', shape = none];
    N;
    Awins [shape = none, label = '1 - k, k'];
    Bwins [shape = none, label = '-k, 1 - k']



     # Connect nodes with edges and labels
    A -> 0 [arrowhead= none]
    A -> B
    A -> 1 [arrowhead = none]
    B -> Accept [headlabel = 'Accept', labeldistance = 5, labelangle=75] 
    B -> N [label = '       Reject']
    N -> Awins [headlabel = 'A wins (1 - p)', labeldistance=4.5 ,
        labelangle=75]
    N -> Bwins [label = 'B wins (p)']
  }

[1]: 'A' 
[2]: '0'
[3]: paste0('Model 3\\n Split 3') 
[4]: paste0('Model 6\\n Split 4') 
")

```
---

```{r, echo=F, eval=T}
library(readxl)

m <- read_excel("/home/redapemusic35/course-materials/R-Certification-Bundle/more-datazips/Children in single-parent families by race.xlsx")

head(m)
```

---

# References

```{r refs, echo=FALSE, results="asis"}
PrintBibliography(myBib)
```

---


